\section{Purpose}
Currently, a problem with dating sites are the lack of genuine connections. Using heteronormative examples,


\subsection{Mens' issues with online dating}

\begin{itemize}
    \item Suffering from poor picture quality
    \item Lack of ability to leverage vocal tonality, body language, and eye contact
\end{itemize}


\subsection{Womens' issues with online dating}
\begin{itemize}
    \item Safety concerns
    \item An overwhelming number of suitors to choose from
    \item An apparent lack of substance from said options
\end{itemize}


\section{Scope}
The scope of this project thus far is to be used as a way to allow men and women to connect based on genuine attributes,
spearheaded by the use of content uploaded by trusted friends.
Specifically, the product would allow friends of a user to upload content such as videos, voice recordings, pictures that describe
how the friend feels about the user, what the friend thinks, etc. 


\section{Overview}
A representative use-case for the product is given below:

\begin{enumerate}
    \item The user signs into \serviceName with their email address and password.
    \item The user defines a list of people that they would like to get references from. 
    \item The references receive an email asking them to upload content onto the requester's profile.
    \item The reference uploads the content.
    \item The reference sees profiles that may be good fits for the requester and makes recommendations.
    \item The recommendee's references get notifications that one of their friends may have a match.
    \item The recommendee's reference confirms the mutual fit.
    \item The user and the match can now message each other.
\end{enumerate}


\section{Reference Material}
\section{Definitions and Acronyms}
\begin{table}[ht]
    \centering
    \begin{tabular}{l | l}
        Term & Definition \\
        \hline
        MVP & Minimum Viable Product \\
        LDA & Leading Dating apps \\
        MS & Matrimony Sites \\
        UGC & User Generated Content \\
    \end{tabular}
    \caption{Table of Definitions and acronyms used}
    \label{tab: def_ac}
\end{table}
% \blindtext[6]